Incentivizing Exploration with Unbiased Histories

### 2018-11-03 main.tex
.
title
Expanded title notes.

%index on the tape
\def\z{\tau}
\title{Incentivizing Exploration with Unbiased History}

\author{
Nicole Immorlica \thanks{Microsoft Research, email: nicimm@microsoft	.com.}
\and
Jieming Mao \thanks{University of Pennsylvania, email: maojm517@gmail.com.}
\and
Aleksandrs Slivkins  \thanks{Microsoft Research, email: slivkins@microsoft.com.}
\and
Zhiwei Steven Wu  \thanks{University of Minnesota, email: zsw@umn.edu.}
}
\begin{document}
\begin{titlepage}
\maketitle

>>>>

%index on the tape
\def\z{\tau}
\title{Incentivizing Exploration with Unbiased Histories}

\author{
Nicole Immorlica \thanks{Microsoft Research, Cambridge, MA. Email: nicimm@microsoft.com.}
\and
Jieming Mao \thanks{University of Pennsylvania, Philadelphia, PA. email: maojm517@gmail.com. Results in this paper were obtained while J. Mao was an intern at Microsoft Research NYC.}
\and
Aleksandrs Slivkins  \thanks{Microsoft Research, New York, NY. email: slivkins@microsoft.com.}
\and
Zhiwei Steven Wu  \thanks{University of Minnesota, Minneapolis, MN. Email: zsw@umn.edu. Results in this paper were obtained while Z.S. Wu was a postdoc at Microsoft Research NYC.}
}
\begin{document}
\begin{titlepage}
\maketitle
